### 2012-02-17 2.1.3.tex
Rearranged and some writing on 2-5.

There is a long-standing debate concering whether English [ŋ] is a phoneme in its own right, demanded by Kiparsky's Alternation Condition \citep{Kiparsky1968} or Lexicon Optimization \citep[][53]{OT}, or simply the allophone of /n/ found before /k, g/ \citep[][65]{Borowsky1986}. The strongest piece of evidence for the pure allophonic analysis (and an attentant process of /g/-\textsc{Deletion}) is the general absence of onset [ŋ], a position where it can never be followed by a dorsal consonant needed to derive the velar allophone. \citet{Pierrehumbert1994} assumes the pure allophonic analysis in her study of syllable contact clusters, and it is adopted here and formalized below in \S\ref{cnpasection}.
%\citealt[][62]{Halle1985a}),

@@

I assume that the front onglide is not part of the onset except in the case where the onset would ortherwise be null (e.g., \emph{jun}[j]\emph{or}). %\footnote{English glides are transcribed here as full segments, not as ``subsegments'', as this distinction does not appear to be meaningful for English, or empirically motivated for other languages \citep{Rubach2002}.}
When [j] is a simplex onset, it may be followed by any vowel \citep[][276]{Borowsky1986}. However, when [j] is immediately preceded by an onset consonant (e.g., [bj]\emph{ugle}), the following vowel is always [u\lm]. This defective distribution of vowels following [j] follows if the onglide in this context is the first component of a phonological diphthong, and thus part of the nucleus (\citealp[][232]{Hayes1980}, \citealp[][61f.]{Harris1994}). External support for this account comes from the fact that in words like \emph{spew}, [ju\lm] may act as a ``unit'' in language games \citep{Nevins2003,Idsardi2005}, to the exclusion of the rest of preceding consonants. Finally, \citet[][42]{Clements1983} note 
that /m, v/ do not appear in onset clusters except in words like \emph{muse} or \emph{view}, in which I assume the glide is nuclear.

@@

The selective properties of the back onglide [w] contrast sharply with those of the front onglide, and I assume that it is assigned to the onset. Whereas the front onglide shows only limited selectivity for preceding tautosylalbic consonants \citep{Kaye1996}, the back onglide [w] is rarely preceded by tautosyllabic consonants other than [k] (e.g., \emph{tran}[kw]\emph{il}). Unlike the front glide, syllable-initial [kw] may be followed by any vowel.
%Whereas [Cju\lm] syllables attracts stress, [kwV] syllables do not \citep[][162f.]{Davis1995}.

>>>>

There is a long-standing debate regarding whether English [ŋ] is a phoneme in its own right, as demanded by Kiparsky's Alternation Condition \citep{Kiparsky1968} or Lexicon Optimization \citep[][53]{OT}, or simply the allophone of /n/ found before /k, g/ \citep[][65]{Borowsky1986}. The strongest piece of evidence for the pure allophonic analysis (and an attentant process of /g/-\textsc{Deletion}) is the general absence of onset [ŋ], a position where it can never be followed by a dorsal consonant needed to derive the velar allophone. \citet{Pierrehumbert1994} assumes the pure allophonic analysis in her study of syllable contact clusters, and it is adopted here and formalized below in Section \ref{cnpasection}.
%\citealt[][62]{Halle1985a}),

@@

I assume that the [j] onglide in words such as \emph{ass}[j]\emph{ume} is present in underlying representations (e.g., \citealt[][278]{Borowsky1986}, J. \citealt{Anderson1988b}, pace \emph{SPE}:196, \citealt[][89]{Halle1985a}, \citealt[][217]{McMahon1990}). The primary motivation for this assumption is the observation that presence or absence of this glide is contrastive (e.g. \emph{coup} $\sim$ \emph{queue}, \emph{booty} $\sim$ \emph{beauty}). I further assume that the front glide is not part of the onset except in the case where the onset would ortherwise be null (e.g., \emph{jun}[j]\emph{or}).
%\footnote{English glides are transcribed here as full segments, not as ``subsegments'', as this distinction does not appear to be meaningful for English, or empirically motivated for other languages \citep{Rubach2002}.}
When [j] is a simplex onset, it may be followed by any vowel \citep[][276]{Borowsky1986}. However, when [j] is immediately preceded by an onset consonant (e.g., [bj]\emph{ugle}), the following vowel is always [u\lm]. This defective distribution of vowels following [j] follows if the onglide in this context is the first component of a phonological diphthong, and thus part of the nucleus (\citealp[][232]{Hayes1980}, \citealp[][61f.]{Harris1994}, \citealp{Davis1995}). \citet[][42]{Clements1983} note that /m, v/ do not appear in onset clusters except in words like \emph{muse} or \emph{view}; the exceptionality of [ju\lm] also suggests the glide is nuclear. There is a great deal of external support for this position as well. The [ju\lm] in words like \emph{spew} may pattern together
in Pig Latin \citep{Davis1995,Idsardi2005} and \emph{shm}-reduplication \citep{Nevins2003}, to the exclusion of the rest of preceding tautosyllabic consonants. The same fusion of [ju\lm] at the expense of the onset is also found in speech errors, e.g., [kju\lm]\emph{mor homponent} for [hju\lm]\emph{mor component} \citep[][130]{Shattuck-Hufnagel1986}. Finally, \citet{Buchwald2005} considers [j] onglides in the speech of VBR, an aphasic patient who has difficulties producing complex onsets.

\ex VBR's complex onsets \citep[79--80, his transcriptions]{Buchwald2005}: \\
\begin{tabular}{l l l}
a. & kəræb  & `crab'  \\
   & bəlid  & `bleed' \\
b. & kəwin  & `queen' \\
   & kəwoʊt & `quote' \\
c. & kut    & `cute'  \\
   & musɪk  & `music  \\ 
\end{tabular}
\xe

\noindent
VBR breaks up complex onsets, including back onglide clusters in (\nextx b). However, in (\nextx c), which contain the front onglide in standard English, no epenthesis occurs: the glide is simply absent. This also suggests that the front onglide is part of the onset, not the nucleus.

@@

The selective properties of the back onglide [w] contrast sharply with those of the front onglide, and I assume that it is assigned to the onset. Whereas the front onglide shows only limited selectivity for preceding tautosyllabic consonants \citep{Davis1995,Kaye1996}, the back onglide [w] is rarely preceded by tautosyllabic consonants other than [k] (e.g., \emph{tran}[kw]\emph{il}). Unlike the front glide, syllable-initial [kw] may be followed by nearly any vowel \citep[][161]{Davis1995}. Unlike [ju\lm], onglide [w] followed by a vowel does not pattern together in Pig Latin \citep[][166]{Davis1995}.

%Whereas [Cju\lm] syllables attracts stress, [kwV] syllables do not \citep[][162f.]{Davis1995}.

### 2012-02-17 2.2.1.tex
Spacing in appendices.
Rearranged and some writing on 2-5.

Before the dawn of generative phonology, many linguists concerned themselves with documenting co-occurrence in various languages. \citet[][28]{Vogt1954} declares that a ``phonemic description of a language \ldots should also comprise a description of the phoneme combinations that occur or may be expected to occur in the language''. Studies in this tradition include the discussions of consononantal co-occurrence in Arabic and Javanese by \citet{Greenberg1950} and \citet{Uhlenbeck1950}, respectively. In the case of \citet{Greenberg1950}'s study, the primary generalization has no exceptions, but \citeauthor{Uhlenbeck1950}'s description of co-occurrence restrictions contains many exceptions. Many years later, \citet{Mester1988} revisits \citeauthor{Uhlenbeck1950}'s study and suggests a statistical method to distinguish between accidental and structural lexical dispreferences in the Javanese lexicon.

\citeauthor{Mester1988}'s technique, which has been adopted by many subsequent studies (e.g., \citealt{Padgett1992,Padgett1995} on Russian; \citealt{Pierrehumbert1993}, \citealt{Frisch1996}, and \citealt{Frisch2004} on Arabic; \citealt{Berkley1994b,Berkley1994a,Berkley2000}, \citealt{Dmitrieva2008a}, \citealt{Dmitrieva2008b} on English), is based on the chi-square test.

In this study, I use the Fisher exact test, which is isomorphic to this chi-square test. The chi-square test has been favored historically simply because it can be easily computed by hand, but it is equally easy to perform either test on a modern computer. Compared to the Fisher test, which is appropriate for small samples or rare events, the chi-square test has a serious defect, since it depends on an approximation which is only exact in the limit (i.e., with a hypothetically infinite sample), and therefore is not appropriate for small samples \citep[e.g.,][142]{Mester1988}.

The opposite problem, difficulties scaling to large samples, is an unfortunate defect of the Monte Carlo procedure developed by \citet{Kessler2001} and applied to co-occurrence statistics by \citet{Martin2007,Martin2011} and \citet{Brown2010}. This technique, which is the Monte Carlo isomorph of the one-tailed chi-square test, depends on the ability to generate random (i.e., unbiased) permutations of large lists. This is much more difficult than prior researchers have realized, as I explain below; less mathematically inclined readers may wish to skip ahead.

Any permutation of a list $L$ can be thought of as a list $S$ such that

$S_i$ 
the $i$th element in the permuted list is

the permuted position of the $i$th elemnt of $L$. Since

A permutation of a list of length $N$ can be thought of a vector $S$ such that $S_i$ is a counting number denoting the length of k

as a list of $N$ unique counting numbers which are less than or equal to $N$;

$N - 1$

The problem is that even for moderately-sized lists, the number of possible permutations quickly exceeds modern computational capabilities.

To explain why this is so requires a short discussion of

The pseudo-random number generator used by both \citeauthor{Martin2011} and \citeauthor{Brown2010} has a ``period'' of approximately $2 ^ 48$; this means that it repeats the same 281-trillion number pattern indefinitiely.

. What this means has a period of approximately $2 ^ 48$. What this means has a period of approximately $2 ^ 48$. What this means has a period of approximately $2 ^ 48$. What this means

use the Perl scripting language, which generally provides a pseudo-random number generator

Both

A list of $N$ elements has $N!$ different permutations. T

When $N$ is large, t
When $N$ is large, current computational

this greatly exceeds the abilities of the pseudorandom number generators

This often a collosal quantity

When $N$ is large, this is a collosal quantita

with a ``period'' of approximately $2 ^ 48$, i.e., it will repeat itself after

I had a chance to write out my thoughts about the periodicity issue for Kessler's Monte Carlo method, and do a bit of research into Perl resources.

%If you're lucky, you have a version of Perl that uses the drand48 library function. The period is 2 ^ 48, around 281 trillion; after 281 trillion draws, it just regenerates the same 281 trillion numbers in the same order.

%A permutation of a list of N items can be thought of as a list of N - 1 random numbers; this is N - 1 because there's only one way to "permute" a one-element list (and in your method, only one outcome for the last element left).

%Given a period P, there are only P unique sequences of random numbers. Unfortunately, even for N = 18, N!, the number of possible permutations is far larger than the period of the Perl random number generator. That means there are many random permutations that can never be generated. When N gets significantly larger, virtually all random permutations can never be reached. In your CELEX compound study, for instance, N = 4758, and thus requires a period of approximately 2 ^ 51260 according to the Stirling approximation. But Perl can only reach 2 ^ 48 of them, a tiny fraction thereof.

%I only have browsed Kessler's book, but I saw that he spoke about how hard it was to calculate the Fisher exact test. With all due respect, I think he's just wrong. It's difficult to compute a p-value via Monte Carlo test that is provably unbiased (for instance, I'm unaware of any publically-available pseudo-random number generator with a period big enough for the CELEX compounds study), but the Fisher exact test, the one-tailed variant of which is isomorphic to the shuffle test, can be computed in the blink of an eye in any good stats environment.

 which in turn requires

Since totally-identical consonants occur quite frequently,

\ex Javanese root co-occurrence (\citealp[][264]{Uhlenbeck1950}, \citealp[][139]{Mester1988}): \vspace{6pt} \\
\begin{tabular}{l r r r r}
\toprule
                      & attested & unattested & saturation & $p$-value \\
\midrule
Same major place      & 21       & 15         & 0.583      & \multirow{2}{*}{6.10\e{-06}} \\
Different major place & 134      & 12         & 0.918 \\
\bottomrule
\end{tabular}
\xe

\noindent
It is evident that roots with identical labial stops are far more common than those in which the roots disagree in voicing. This data is input to a chi-square test, which reports that this highly skewed distribution is unlikely to be due to chance ($\chi^2 = 64.525$, two-tailed $p = 9.5$\e{-16}).

\citep[see also][]{Gorman2012}
contains the counts

%\ex $ \lim_{n \rightarrow \infty} n! = 2 ^ {(n \ln{n} - n) \cdot \log_2{e}} $ \xe

@@

Applying the syllabification algorithm to the CELEX data produces 40 medial onset types and 22 medial coda types from 161 medial consonant clusters.

It must be stressed that under current assumptions, this is independent of whether predictable prosodic representations (particularly coda and onset identity) are part of the memorized underlying representation \citep[e.g.,][]{Vaux2003}.

It is an undeniable fact that URs need to be

The derivative nature of 
W

\citet{Ito1989a,Noske1993}

The nature of 
The prosodic characteristic of

The Fisher exact test is isomorphic to the chi-square test

and has been used by several researchers \citep{Zuraw2010}.

Unlike the chi-square test, which uses an approximation which is exact in the limit (i.e., only with a hypothetical infinite sample), the Fisher exact test is robust to small sample sizes.

The opposite problem, inability to scale to large samples, is a defect of the a statistical procedure developed by \citet{Kessler2001} and applied to co-occurrence restrictions by \citet{Martin2007,Martin2011}. This procedure is a Monte Carlo approach to t

Under a one-tailed test, the alternative hypothesis is underrepresentation, whereas a two-tailed test also allows the possibility that a class of clusters would be overrepresented, i.e., more frequent than predicted by the null hypothesis. As

@@

English has a process of voice assimilation which is found in two inflectional suffixes. The suffix /-d/ forms regular pasts and denominal adjectives, and /-z/ forms regular noun plurals and genitives, and the 3sg. present active indicative verbs.\footnote{The URs /-d, -z/ are argued for by \citet[][282]{Hockett1958}, \citet[][210]{SPE}, \citet{Basboll1972}, \citet{Shibatani1972}, \citet[][]{Anderson1973a}, \citet[][102]{Pinker1988}, and \citet[][284f.]{Bakovic2005b}, and alternative views are presented by \citet[][211f.]{LANGUAGE}, \citet[][426]{Nida1948}, \citet{Luelsdorff1969}, \citet{Lightner1970}, \citet{Hoard1971}, \citet[]{Miner1975}, \citet{Zwicky1975}, \citet{Kiparsky1985}, and \citet[][135]{Borowsky1986}.}

@@

\ex Artificial language adaptations \citep[][394]{Wright1975}: \\
\begin{tabular}{l l l l l l}
a. & [gownp]    & > & [gump] \\
b. & [\v{j}umg] & > & [\v{j}úŋgə] \\
c. & [ðʌŋd]     & > & [tɔŋg] \\
\end{tabular} 
\xe

\noindent
If this game is akin to the process of loanword adaptation, it is possible that various extragrammatical pressures are at play \citep[e.g.,][]{Halle1998b,Dupoux1999,Ussishkin2003,Peperkamp2008}. Yet, the independent evidence for a phonological process of nasal place assimilation provides the most parsiminious account of the adaptations seen in \citeauthor{Wright1975}'s study.

@@

\ex Degemination in the /-t/ past (\citealp[][105]{Halle1985a}, \citealp[][492]{Myers1987}): \vspace{6pt} \\
\begin{tabular}{l l l l l}
a. & /bɛnd-t/ & \arrow & [bɛnt] & (cf. \emph{burn}[t]) \\
b. & /bɪld-t/ & \arrow & [bɪlt] & (cf. \emph{spil}[t]) \\
\end{tabular}
\xe

>>>>

Before the dawn of generative phonology, many linguists concerned themselves with documenting co-occurrence in various languages. \citet[][28]{Vogt1954} declares that a ``phonemic description of a language \ldots should also comprise a description of the phoneme combinations that occur or may be expected to occur in the language''. Studies in this tradition include the discussions of consononantal co-occurrence in Arabic and Javanese by \citet{Greenberg1950} and \citet{Uhlenbeck1950}, respectively. \citeauthor{Uhlenbeck1950}, for instance, puts forth co-occurrence dispreferences, rather than exceptionless generalizations of the sort given by \citet{Greenberg1950}. Years later, \citet{Mester1988} revisits \citeauthor{Uhlenbeck1950}'s study and proposes a statistical technique, based on the chi-square test, to distinguish between accidental and structural lexical dispreferences in the Javanese lexicon.

\citeauthor{Mester1988}'s technique has been adopted by many subsequent studies (e.g., \citealt{Padgett1992,Padgett1995} on Russian; \citealt{Pierrehumbert1993}, \citealt{Frisch1996}, and \citealt{Frisch2004} on Arabic; \citealt{Berkley1994b,Berkley1994a,Berkley2000}, \citealt{Dmitrieva2008a}, \citealt{Dmitrieva2008b} on English). The null hypothesis $H_0$ is that some sequence occurs at no different a rate than the researcher expects, and the alternative hypothesis $H_1$ is that it is underrepresented. Given an observed frequency $O$ and also a frequency $E$ expected under the null hypothesis, the test is as follows.

\ex $\displaystyle \textrm{Reject } H_0 \textrm{ iff } \frac{(O E) ^ 2}{E} >
\chi^2$ \xe

%\footnote{This is the one-tailed version of the test.}

In this study, I use the \citet{Fisher1934} exact test, which is isomorphic to this chi-square test. Compared to the chi-square test, the Fisher exact test $p$-value is somewhat more difficult to compute, but both are automated by modern statistical packages and can be computed rapidly. The major advantage of the Fisher test over the chi-square test is that it is appropriate for small samples or rare events, whereas the chi-square test depends on an approximation which is only exact in the limit (i.e., with a hypothetically infinite sample), and therefore is not appropriate for small samples \citep[see][]{Gorman2012a}.
%\citep[e.g.,][142]{Mester1988}.

On the other end of the spectrum, the Monte Carlo statistical procedure developed by \citet{Kessler2001} and applied to co-occurrence statistics by \citet{Martin2007,Martin2011} and \citet{Brown2010} does not scale to large samples. The Monte Carlo procedure is isomorphic to the one-tailed Fisher Exact test, and involves comparing observed co-occurrence counts to those produced by randomly generated samples.  This requires the researcher to generate random permutations, something which is particularly difficult for large samples, as I will explain; disinterested readers may wish to skip the following paragraph.

Any permutation of a sequence $L$ can be represented as a sequence $S$ of the same length, where the value of $S_i$ corresponds to the permuted position of $L_i$. Generating random permutations requires an unbiased method to generate all $N!$ of these lists with equal probability. Unfortunately, this is near impossible for $N$s of moderate size with current computational resources. Any pseudo-random number generator can be characterized by its ``period'', the number of pseduo-random numbers it can emit before repeating itself; this is also the upper limit for the number of random permutations that can be generated. The pseudo-random number generator used by both \citeauthor{Martin2011} and \citeauthor{Brown2010} has a period of approximately $2^{48}$, a number which turns out to be smaller than $17!$. For the large samples, sometimes in the thousands, used by these researchers, virtually all the possible permutations can never be generated by this method. As a consequence, the shuffling procedure is far from random and introducing the possibility that the statistical test is biased in unpredictable ways.

As an example of the Fisher exact test as it is applied here, consider some of the Javanese co-occurrence facts considered by \citet{Mester1988}. \citeauthor{Mester1988} is at pains to show that there is a gradient dispreference for first and second root consonants which share the same major place. However, perfectly identical first and second consonants are exempt. Since

% APPLY THIS TO JAVANESE

\ex Javanese root co-occurrence (\citealp[][264]{Uhlenbeck1950}, \citealp[][139]{Mester1988}): \vspace{6pt} \\
\begin{tabular}{l r r r r}
\toprule
           & attested & unattested & saturation & $p$-value \\
\midrule
conforming & 134      & 12         & 0.918      & \multirow{2}{*}{6.095\e{-06}} \\
violating  & 21       & 15         & 0.583 \\
\bottomrule
\end{tabular}
\xe

\noindent
It is evident that roots with identical labial stops are far more common than those in which the roots disagree in voicing.

This data is input to a chi-square test, which reports that this highly skewed distribution is unlikely to be due to chance

That this is highly unlikely to be due to chance is apparent both from the chi-square ($\chi^2 = 25.572$, two-tailed $p = 4.3$\e{-07}) and Fisher exaact tests ($p =  6.095$\e{-06}).

I use two-tailed statistical tests throughout. 
Under a one-tailed test, the alternative hypothesis is underrepresentation, whereas a two-tailed test also allows the possibility that a class of clusters would be overrepresented, i.e., more frequent than predicted by the null hypothesis. As

@@

It must be stressed that under current assumptions, this is independent of whether predictable prosodic representations (particularly coda and onset identity) are part of the memorized underlying representation \citep[e.g.,][]{Vaux2003}.
It is an undeniable fact that URs need to be 
The derivative nature of 
\citet{Ito1989a,Noske1992}

@@

English has a process of voice assimilation which is found in two inflectional suffixes. The suffix /-d/ forms regular pasts and denominal adjectives, and /-z/ forms regular noun plurals and genitives, and the 3sg. present active indicative verbs.\footnote{The URs /-d, -z/ are argued for by \citet[][282]{Hockett1958}, \citet[][210]{SPE}, \citet{Basboll1972}, \citet{Shibatani1972}, S. \citet[][]{Anderson1973a}, \citet[][102]{Pinker1988}, and \citet[][284f.]{Bakovic2005b}, and alternative views are presented by \citet[][211f.]{LANGUAGE}, \citet[][426]{Nida1948}, \citet{Luelsdorff1969}, \citet{Lightner1970}, \citet{Hoard1971}, \citet[]{Miner1975}, \citet{Zwicky1975}, \citet{Kiparsky1985}, and \citet[][135]{Borowsky1986}.}

@@

\ex Artificial language adaptations \citep[][394, his transcriptions]{Wright1975}: \\
\begin{tabular}{l l l l l l}
a. & [gownp] & > & [gump] \\
b. & [ǰumg]  & > & [ǰúŋgə] \\
c. & [ðʌŋd]  & > & [tɔŋg] \\
\end{tabular} 
\xe

\noindent
If this game is akin to the process of loanword adaptation, it is possible that various extragrammatical pressures are at play \citep[e.g.,][]{Halle1998b,Dupoux1999,Ussishkin2003,Peperkamp2008}. Yet, the independent evidence for a phonological process of nasal place assimilation provides the most parsiminious account of the adaptations seen in \citeauthor{Wright1975}'s study. J. \citet{Myers1993} also shows that \textsc{Coda Nasal Place Assimilation} is fed by speech errors:

\ex Speech errors and \textsc{Coda Nasal Place Assimilation} \citep[][228]{Myers1993}: \\
\begin{tabular}{l l l}
   & \emph{error}  & \emph{target} \\
a. & primps        & prints        \\
b. & rand orker    & rank order    \\
%  & [sprɪg]time for [hɪ̃ntlɘr] & springtime for Hitler \\
c. & po[ŋ]cutation & computation   \\
\end{tabular}
\xe

@@

\ex Degemination in the /-t/ past (\citealp[][105]{Halle1985a}, S. \citealp[][492]{Myers1987}): \vspace{6pt} \\
\begin{tabular}{l l l l l}
a. & /bɛnd-t/ & \arrow & [bɛnt] & (cf. \emph{burn}[t]) \\
b. & /bɪld-t/ & \arrow & [bɪlt] & (cf. \emph{spil}[t]) \\
\end{tabular}
\xe

### 2012-02-17 2.2.3.tex
Rearranged and some writing on 2-5.

\ex $\displaystyle f(r~; C, \alpha) = \frac{C}{r^\alpha}$ \xe

@@

That clusters (and the codas and onsets that make them up conforms to Zipf's law is not itself a deep observation. Zipfian distributions are characteristic of both syntactic rules \citep{Yang2009}, but also $n$-grams \citep{Baroni2009} and of randomly-generated texts \citep{Miller1957,Li1992}. The import of this statistical property for the study of cluster phonotactics is that it makes it difficult, on statistical grounds alone, to determine which unobserved events are excluded, and which are accidentally missing.

>>>>

\ex $\displaystyle f(r; C, \alpha) = \frac{C}{r^\alpha}$ \xe

@@

That clusters (and the codas and onsets that make them up conforms to Zipf's law is not itself a deep observation. Zipfian distributions are characteristic of both syntactic rules \citep{Yang2009}, but also $n$-grams \citep{Baroni2009} and of non-linguistic symbol systems \citep{Chomsky1958,Sproat2010} or randomly-generated texts \citep{Miller1957,Li1992}. The import of this statistical property for the study of cluster phonotactics is that it makes it difficult, on statistical grounds alone, to determine which unobserved events are excluded, and which are accidentally missing.
